Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-15 doc/GMP2015/s08_pinnedline.tex
Fixed image and moved proof of lemma to appendix.

\begin{definition} %[2-Dimensional Pinned Line Incidence Graph] \label{prob:pinned_subspace}
A  graph $G=(V,E, w_V, w_E)$ is a \textbf{2-dimensional pinned line incidence graph},
if  $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$, and
there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
such that $e$ is constrained to lie on a line passing through $x$.
%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$

%Let $X$ be a  set of $m$ pins that are fixed in $\mathbb{R}^2$, and $V$ be the index set of a set of vertices.
%For every pin $x \in X$, we are also given the indices of two vertices $v_1,v_2$ in $V$,
%such that the line (edge) spanned by $v_1$ and $v_2$ must pass through $x$.
% % % % % % % % % % % % % % % % % % %
%Find any such set of points $P$ satisfying the given incidences.
%For every pin $x\in X$, we are also given a line $\supp{x}$, %of %a set of $s$-dimensional subspaces passing through
%i.e, a size-two index subset of an unknown set of points $D = \{v_1,\ldots,v_n\}$ in $\mathbb{R}^2$, %$P = \{p_1,\ldots, p_n \}$,
%such that  $x_i$ lies on the line spanned by $\supp{x}$.
%%assume additionally that
%%no $s$ pins lie on any single subspace defined by one of the above hyperedges.
%Find any such set D %$P[X]$
%that satisfies the given subspace incidences. % specified by $\supp[P]{x}$.%$\{S_i\}$. % on $P[X]$ and $X$.
\end{definition}

\begin{remark}
For 2-dimensional pinned line incidence graphs,
the constant $k$ used in the definition of independence and rigidity is $0$  \cite{xxx} (see Definition~\ref{xxx}--\ref{xxx}).
\end{remark}

In the case of microfibril cross-linking, each fibril is
attached to some fixed larger organelle/membrane at one spot.
Consequently, each fibril can be modeled as an edge of the graph,
with the attachment being the corresponding pin in $X$.
The two cross-linkings on the fibril are modeled as the two vertices in $V$ defining the edge.
%so it can be modeled as an edge/line segment incident at a pin in $X$.
%For cross-linking density 2,
%i.e.\ each fibril has two cross-linkings with other fibrils,
%The cross-linkings can be modeled as vertices in $V$.

@@

\begin{figure}
  \centering
  % \includegraphics[width=.9\linewidth]{img/pinned}
\caption{ A well-constrained pinned line incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

 The \textbf{DR-plan} of  a 2-dimensional pinned line incidence graph $G$ is Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
    \begin{enumerate}
        %\item The root of the tree `contains' $G$.
        \item[2] For any node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item[4] A node containing a single edge is a leaf.
    \end{enumerate}
\end{definition}

@@

\begin{lemma}
\label{lem:pinned_union_intersection}
Let $F_i$ and $F_j$ to be subgraphs of the same well-constrained graph $F$,
where each of them can be either  a single edge or a connected well-constrained subgraph.
There are only two possible cases:
\begin{itemize}
\item At least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is under-constrained, if and only if $F_i \cap F_j$ is a vertex.
\item Both $F_i$ and $F_j$ are well-constrained, if and only if $F_i \cup F_j$ is well-constrained, if and only if $F_i \cap F_j$ is well-constrained.
\end{itemize}

%The following table summarizes all bijections:
%\setlength{\tabcolsep}{3pt}
%{\small
%\begin{center}
%\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
%\hline
%\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
% \centering--- &  \sout{over-constrained}          &  \centering --- \tabularnewline \hline
%at least one of $F_i,F_j$ is an edge & under-constrained       &  \centering a vertex (under-constrained)  \tabularnewline \hline
%both $F_i$ and $F_j$ are well-constrained & well-constrained        &  \centering well-constrained  \tabularnewline \hline
% \centering --- & ---                     &  \centering \sout{under-constrained} \tabularnewline \hline
%\end{tabular}
%\end{center}
%}
%\setlength{\tabcolsep}{6pt}

\end{lemma}

%The proof of Lemma~\ref{lem:pinned_union_intersection} is similar to the proofs of Lemma~\ref{t-l1}--\ref{iuc-l1}.

%\begin{lemma}
%Let $F_j$ and $F_j$ be well-constrained subgraphs of the same well-constrained graph $F$.
%Both $F_i \cup F_j$ and $F_i \cap F_j$ can only be well-constrained.
%\end{lemma}
%
%\begin{proof}
%\begin{enumerate}
%\item Obviously $F_i \cup F_j$ cannot be over-constrained since it is a subgraph of well-constrained graph $F$.
%\item $F_i \cup F_j$ cannot be under-constrained, otherwise $F_i \cap F_j$ would be over-constrained while there are no trivial over-constrained graphs.
%\item The only remaining case is that $F_i \cup F_j$ is well-constrained, which is true if and only if $F_i \cap F_j$ is well-constrained.
%\end{enumerate}
%\end{proof}

Proofs of Lemma~\ref{lemma:wc_intersection_is_C} and \ref{corollary:no_edges_between_diff} straightforwardly extend to 2-dimensional pinned line incidence graphs
given Lemma~\ref{lem:pinned_union_intersection} and the modified definition of DR-plan.
Now we  show that Lemma~\ref{lemma:wc_intersection_makes_all_wc} also holds.

\begin{proof}[Proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for 2D pinned line incidence graphs]
We use the same notations as in the original proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} in Section~\ref{sec:infer_parent}.

First notice that since $C_i \cup C_j$ is well-constrained, by Lemma~\ref{lem:pinned_union_intersection},
both $C_i$ and $C_j$ are connected well-constrained vertex-maximal proper subgraphs of  $C$.
Since $C_j \cup C_j = C$, there are no edges in $C$ that is not contained in a well-constrained subgraph, so $C$ does not have any single-edge child node, and $C_k$ is a connected well-constrained vertex-maximal proper subgraph of  $C$.

Then we analyze all the possible cases for $C_k$.
\begin{itemize}
%    \item 4 cases: $C_k$ cannot be $Idc(C,R_i\cup R_j)$, $Idc(C,R'_i\cup R_j)$, $Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$ because these are all disconnected (Corollary~\ref{wc-c1}) and by our modified requirement of DR-plan nodes.
    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since $C_k\cup C_i = Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{lemma:wc_intersection_is_C} that $C_k\cup C_i$ cannot be well-constrained.
    By Lemma~\ref{lem:pinned_union_intersection}, it must be under-constrained,
    so one of $C_i$ and $C_k$ must be an edge, contradicting the assumption that both $C_i$ and $C_k$ are well-constrained.
%    We also know it cannot be trivial because it contains well-constrained subgraphs. This means it must be under-constrained. From Lemma \ref{uc-l1}, we know that $C_k\cap C_i=Idc(C,R'_j\cup D_{i,j})$ must then be trivial. This is impossible because $D_{i,j}$ is well-constrained, thereby contradicting the assumption that $C_k$ is well-constrained.

    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D'_{i,j})$ is not possible. The proof is similar to the previous case.
%    union with $C_i$ (or $C_j$) is not equal to $C$. Therefore, the union must be under-constrained which means the intersection must be trivial (a single node). However, $C_k\cap C_i=Idc(C,R'_j\cup D'_{i,j})$ and since $R'_j$ and $D'_{i,j}$ are not empty sets, it cannot be trivial making a contradiction.

    \item 2 cases: $C_k=Idc(C,R'_i\cup R_j\cup D'_{i,j})$ and $C_k=Idc(C,R_i\cup R'_j\cup D'_{i,j})$ are not possible.
    The proof is similar to the previous case.
    %The proof mirrors the previous case, except you must choose $C_i$ and $C_j$, respectively, here.
\end{itemize}

All the remaining cases are similar to the original proof.

\end{proof}

%How theorems go through when only considering connected rigidity components

The following lemma serves as Lemma~\ref{lemma:uc_intersection_makes_all_uc} for pinned line incidence and can be proved similarly.
\begin{lemma}
\label{lem:vertex_intersection}
If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
\end{lemma}

>>>>

%[2-Dimensional Pinned Line Incidence Graph] \label{prob:pinned_subspace}
A \textbf{2-dimensional pinned line incidence graph}  $G=(V,E, w_V, w_E)$ 
%is a \textbf{2-dimensional pinned line incidence graph},
 has weight functions $w_V(v) = 2, w_E(e) = 1$ for all $v \in V, e \in E$.
Additionally, there is  a  set $X$ of $|E|$ \textbf{pins} with fixed positions in $\mathbb{R}^2$,
such that  %every edge $e \in E$ corresponds to a pin $x \in X$ where
for each edge $e \in E$, there is a uniquely corresponding pin $x \in X$,
such that $e$ is constrained to lie on a line passing through $x$.
%There exists a set $X$ of $|E|$ pins fixed in $\mathbb{R}^2$, such that each edge $e_i$

%Let $X$ be a  set of $m$ pins that are fixed in $\mathbb{R}^2$, and $V$ be the index set of a set of vertices.
%For every pin $x \in X$, we are also given the indices of two vertices $v_1,v_2$ in $V$,
%such that the line (edge) spanned by $v_1$ and $v_2$ must pass through $x$.
% % % % % % % % % % % % % % % % % % %
%Find any such set of points $P$ satisfying the given incidences.
%For every pin $x\in X$, we are also given a line $\supp{x}$, %of %a set of $s$-dimensional subspaces passing through
%i.e, a size-two index subset of an unknown set of points $D = \{v_1,\ldots,v_n\}$ in $\mathbb{R}^2$, %$P = \{p_1,\ldots, p_n \}$,
%such that  $x_i$ lies on the line spanned by $\supp{x}$.
%%assume additionally that
%%no $s$ pins lie on any single subspace defined by one of the above hyperedges.
%Find any such set D %$P[X]$
%that satisfies the given subspace incidences. % specified by $\supp[P]{x}$.%$\{S_i\}$. % on $P[X]$ and $X$.

\begin{remark}
For 2-dimensional pinned line incidence graphs,
the constant $k$ used in the definition of independence and rigidity is $0$  \cite{xxx} (see Section~\ref{sec:prelim_defs}).
\end{remark}

In the case of microfibril cross-linking, each fibril is
attached to some fixed larger organelle/membrane at one spot.
Consequently, each fibril can be modeled as an edge of the graph,
with the attachment being the corresponding pin in $X$.
The two cross-linkings on the fibril are modeled as the two vertices in $V$ defining the edge.

@@

\begin{figure}
  \centering
   \includegraphics[width=.9\linewidth]{img/pinned}
\caption{ A well-constrained 2-dimensional pinned line incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

 The \textbf{DR-plan} of  a 2-dimensional pinned line incidence graph $G$ is Definition~\ref{def:drp} with  modified rules number 2 and 4:
%    The \textbf{decomposition-recombination (DR-) plan} of  a 2-dimensional pinned line incidence graph $G$, $DRP(G)$, is  a tree that has the following properties:
    \begin{enumerate}
        %\item The root of the tree `contains' $G$.
        \item[2] For any non-leaf node $C$, each of its children, $C_1,\ldots,C_N$, is either an edge not contained in any well-constrained proper subgraph of $C$, or a {\em connected} well-constrained vertex-maximal proper subgraph of  $C$.
        %\item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item[4] A node containing a single edge is a leaf.
    \end{enumerate}
\end{definition}

@@

\begin{lemma}
\label{lem:pinned_union_intersection}
Let $F_i$ and $F_j$ to be subgraphs of the same well-constrained graph $F$,
where each of them can be either  a single edge or a connected well-constrained subgraph.
There are only two possible cases:
\begin{itemize}
\item At least one of $F_i$, $F_j$ is an edge, if and only if $F_i \cup F_j$ is under-constrained, if and only if $F_i \cap F_j$ is a vertex.
\item Both $F_i$ and $F_j$ are well-constrained, if and only if $F_i \cup F_j$ is well-constrained, if and only if $F_i \cap F_j$ is well-constrained.
\end{itemize}
%The following table summarizes all bijections:
%\setlength{\tabcolsep}{3pt}
%{\small
%\begin{center}
%\begin{tabular}{|p{2.8cm}|c|p{2.3cm}|}
%\hline
%\textbf{Property of $F_i,F_j$} & \textbf{$F_i\cup F_j$} & \centering \textbf{$F_i\cap F_j$}  \tabularnewline \hline
% \centering--- &  \sout{over-constrained}          &  \centering --- \tabularnewline \hline
%at least one of $F_i,F_j$ is an edge & under-constrained       &  \centering a vertex (under-constrained)  \tabularnewline \hline
%both $F_i$ and $F_j$ are well-constrained & well-constrained        &  \centering well-constrained  \tabularnewline \hline
% \centering --- & ---                     &  \centering \sout{under-constrained} \tabularnewline \hline
%\end{tabular}
%\end{center}
%}
%\setlength{\tabcolsep}{6pt}
\end{lemma}

Given Lemma~\ref{lem:pinned_union_intersection} and the modified definition of DR-plan,
proofs of Lemma~\ref{lemma:wc_intersection_is_C} and \ref{corollary:no_edges_between_diff} straightforwardly extend to 2-dimensional pinned line incidence graphs.
The proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for 2-dimensional pinned line incidence graphs 
is given in Appendix~\ref{sec:appendix_pinned}.
The following lemma serves as Lemma~\ref{lemma:uc_intersection_makes_all_uc} for pinned line incidence and can be proved similarly.
\begin{lemma}
\label{lem:vertex_intersection}
If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
\end{lemma}
